Assessing the Replicability of Psychological Science Through Pedagogy

### 2016-06-24 paper/paper.Rmd
formatting

author-information:
    - \author{Eric Smith*, Robert X. D. Hawkins*, the students of Psych 254, & Michael C. Frank}

@@

```{r global_options, include=FALSE}
rm(list=ls())
library(knitr)
knitr::opts_chunk$set(fig.width=6, fig.height=5, fig.crop = FALSE, 
                      fig.path='figs/', echo=FALSE, warning = FALSE, 
                      cache=FALSE, message = FALSE, sanitize = TRUE)
library(googlesheets)
library(dplyr)
library(xtable)
```

@@

```{r}
project_plan_sheet <- gs_url("https://docs.google.com/spreadsheets/d/1KZw75xlypvtK0cDoOHqXfFd3HsrfJ4gbq8iEJ6LOa0Y", lookup=TRUE) # Need lookup=T to initialize
project_plan_raw <- gs_read_csv(project_plan_sheet)
```

{\small 
```{r, results='asis',  fig.pos = "t", fig.cap = "Summary of attempted replications."}

@@

% latex table generated in R 3.3.0 by xtable 1.8-2 package
% Fri Jun 24 12:02:11 2016
\begin{table}[ht]
\centering
\begin{tabular}{lllllrr}
  \hline
Citation & Expt & Data & Materials & Turk? & N (orig) & N (rep) \\ 
  \hline
@storm2015 & 3 & No & No & No &  48 &  61 \\ 
@lewis2015 & 4 & No & Yes & Yes & 122 & 128 \\ 
@scopelliti2015 & 3 & No & Yes & Yes & 550 & 124 \\ 
@liverence2015 & 1 & No & Some & No &  18 &  \\ 
@wang2015 & 2 & No & No & No & 219 & 397 \\ 
@sofer2015 & 1 & No & Yes & No &  48 &  95 \\ 
@ko2015 & 2 & Yes & Some & No &  40 &  40 \\ 
@dunning2015 & 1b & No & Yes & Yes & 202 &  50 \\ 
@proudfoot2015 & 1 & No & No & Yes &  80 &  84 \\ 
@zaval2015 & 1 & Yes & Yes & Yes & 312 & 328 \\ 
@franconeri2015 & 1a & No & No & No &  12 &  27 \\ 
   \hline
\end{tabular}
\caption{Summary of attempted replications} 
\label{tab:summary}
\end{table}

@@

We eventually used a hybrid, case-by-case selection criterion that attempted to maximize the success of the project while staying within the constraints of our budget.^[We initially were allocated $1,500 but one student contributed personal research funds, leading to a total cost of \approx $1,700 for all studies. We attempted to set payment for our studies at approximately $6/hour based on timing estimated from pilot A sessions.] In `{r} sum(project_plan$power_standard == "80% power")} cases, we powered the replication attempt to 80% post-hoc power. In `{r} sum(project_plan$power_standard == "Original")` cases, we used the original sample size. In one case, the original experiment was apparently extremely over-powered in the post-hoc analysis, so we chose a smaller sample size that still would apparently yield high power.  In one case, we reduced the number of trials as part of the adaptation to mechanical turk, and in one case of a multi-step procedure where the first step consisted of stimulus generation, we decreased the N in the first stage of the procedure (details available in Supplemntal Materials).

@@

Details of individual replications are available in the supplementary materials. Students chose findings from a wide variety of domains for replication. One group was nvestigations of memory and visual attention [e.g., @franconeri2015], including in applied contexts like remembering "deleted" files [@storm2015] or tracking transition between locations on smartphone apps [@liverence2015]. A second cluster came from studies of social perception, including judgments of faces and voices [@ko2015;@sofer2015], as well as studies of attributions of modesty, creativity, and expertise [@atir2015;@scopelliti2015;@proudfoot2015]. Other studies investigated increasing retirement savings by orienting participants to the future [@lewis2015], legacy priming [@zaval2015], and the effects of math anxiety on performance [@wang2015].

>>>>

author-information:
    - \author{Eric Smith*, Robert X. D. Hawkins*, the students of Psych 254, and Michael C. Frank}

@@

```{r global_options, include=FALSE}
rm(list=ls())
library(knitr)
knitr::opts_chunk$set(fig.width=6, fig.height=5, fig.crop = FALSE, 
                      fig.path='figs/', echo=FALSE, warning = FALSE, 
                      cache=TRUE, message = FALSE, sanitize = TRUE)
library(googlesheets)
library(dplyr)
library(xtable)
```

@@

```{r, results='asis'}
project_plan_sheet <- gs_url("https://docs.google.com/spreadsheets/d/1KZw75xlypvtK0cDoOHqXfFd3HsrfJ4gbq8iEJ6LOa0Y", lookup=TRUE) # Need lookup=T to initialize
project_plan_raw <- gs_read_csv(project_plan_sheet)

@@

% latex table generated in R 3.3.0 by xtable 1.8-2 package
% Fri Jun 24 12:02:11 2016
\begin{table}[ht]
\centering
\begin{tabular}{lllllrr}
  \hline
Citation & Expt & Data & Materials & Turk? & N (orig) & N (rep) \\ 
  \hline
@storm2015 & 3 & No & No & No &  48 &  61 \\ 
@lewis2015 & 4 & No & Yes & Yes & 122 & 128 \\ 
@scopelliti2015 & 3 & No & Yes & Yes & 550 & 124 \\ 
@liverence2015 & 1 & No & Some & No &  18 &  \\ 
@wang2015 & 2 & No & No & No & 219 & 397 \\ 
@sofer2015 & 1 & No & Yes & No &  48 &  95 \\ 
@ko2015 & 2 & Yes & Some & No &  40 &  40 \\ 
@dunning2015 & 1b & No & Yes & Yes & 202 &  50 \\ 
@proudfoot2015 & 1 & No & No & Yes &  80 &  84 \\ 
@zaval2015 & 1 & Yes & Yes & Yes & 312 & 328 \\ 
@xu2015 & 1a & No & No & No &  12 &  27 \\ 
   \hline
\end{tabular}
\caption{Summary of attempted replications} 
\label{tab:summary}
\end{table}

@@

We eventually used a hybrid, case-by-case selection criterion that attempted to maximize the success of the project while staying within the constraints of our budget.
^[We initially were allocated \$1,500 but one student contributed personal research funds, leading to a total cost of $\approx$ \$1,700 for all studies. We attempted to set payment for our studies at approximately \$6/hour based on timing estimated from pilot A sessions.] 
In 
`{r} sum(project_plan$power_standard == "80% power")} 
cases, we powered the replication attempt to 80\% post-hoc power. In 
`{r} sum(project_plan$power_standard == "Original")` 
cases, we used the original sample size. In one case, the original experiment was apparently extremely over-powered in the post-hoc analysis, so we chose a smaller sample size that still would apparently yield high power.  In one case, we reduced the number of trials as part of the adaptation to mechanical turk, and in one case of a multi-step procedure where the first step consisted of stimulus generation, we decreased the N in the first stage of the procedure (details available in Supplemntal Materials).

@@

Details of individual replications are available in the supplementary materials. Students chose findings from a wide variety of domains for replication. One group was nvestigations of memory and visual attention [e.g., @xu2015], including in applied contexts like remembering "deleted" files [@storm2015] or tracking transition between locations on smartphone apps [@liverence2015]. A second cluster came from studies of social perception, including judgments of faces and voices [@ko2015;@sofer2015], as well as studies of attributions of modesty, creativity, and expertise [@atir2015;@scopelliti2015;@proudfoot2015]. Other studies investigated increasing retirement savings by orienting participants to the future [@lewis2015], legacy priming [@zaval2015], and the effects of math anxiety on performance [@wang2015].
